---
title: "Example input for slides"
output: ioslides_presentation
runtime: shiny
---

```{r install, eval=FALSE, include=FALSE}
devtools::install_github("rstudio/crosstalk")
devtools::install_github("jcheng5/d3scatter")
devtools::install_github("rstudio/leaflet")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(dplyr)
library(forcats)
library(shiny)
library(crosstalk)
library(leaflet)
library(d3scatter)
library(ggplot2)
library(plotly)
library(leaflet)
library(DT)
data(quakes)
data(iris)
data(mtcars)
data(cars)
data(pressure)
data(diamonds)
data(faithful)
```

## Text

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Plot

```{r pressure}
plot(pressure)
```

## ggplot2: scatter

```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point(aes(color = class)) +
  geom_smooth(se = FALSE, method = "loess") +
  labs(
    title = "Fuel efficiency generally decreases with engine size",
    subtitle = "Two seaters (sports cars) are an exception because of their light weight",
    caption = "Data from fueleconomy.gov"
  )
```

## ggplot2: facets

```{r}
ggplot(diamonds, aes(carat, price)) + 
  geom_hex(bins = 20) + 
  facet_wrap(~cut_number(depth, 6))
```

## htmlwidgets: leaflet

```{r htmlwidgets}
leaflet(quakes[1:20,]) %>% 
  addTiles() %>%
  addMarkers(~long, ~lat, popup = ~as.character(mag))
```

## htmlwidgets: plotly

```{r}
p <- ggplot(data = diamonds, aes(x = cut, fill = clarity)) +
            geom_bar(position = "dodge")
ggplotly(p)
```

## htmlwidgets: datatable

```{r}
datatable(iris, options = list(pageLength = 5))
```

## htmlwidgets: crosstalk

```{r crosstalk}
shared_mtcars <- SharedData$new(mtcars)
bscols(widths = c(3,NA,NA),
  list(
    filter_checkbox("cyl", "Cylinders", shared_mtcars, ~cyl, inline = TRUE),
    filter_slider("hp", "Horsepower", shared_mtcars, ~hp, width = "100%"),
    filter_select("auto", "Automatic", shared_mtcars, ~ifelse(am == 0, "Yes", "No"))
  ),
  d3scatter(shared_mtcars, ~wt, ~mpg, ~factor(cyl), width="100%", height=250),
  d3scatter(shared_mtcars, ~hp, ~qsec, ~factor(cyl), width="100%", height=250)
)
```

## Shiny

```{r, echo = FALSE}
sliderInput("bins", "Number of bins:", min = 1, max = 50, value = 30)

renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)

  # draw the histogram with the specified number of bins
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```
